\documentclass{article}

% Set the margins of the page.
\usepackage[a4paper, total={6in, 8in}]{geometry}

% A bunch of math packages.
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{mathtools}

% Insert images
\usepackage{graphicx}

% COLORS!
\usepackage{color}

% More enumerate types such as \alph*
\usepackage{enumitem}

% Used for code-blocks in latex.
\usepackage{listings}

% Create links when using ref and table of contents.
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=black}

% Replace the indents for paragraphs with empty lines.
\usepackage[parfill]{parskip}

% Number equations with reference to sub sections.
\numberwithin{equation}{subsection}

\definecolor{lightgray}{RGB}{200, 200, 200}

% Set some style rules for code-blocks
\lstset{
	literate={<-}{$\leftarrow$}{2} {\\infty}{$\infty$}{1},
	backgroundcolor=\color{lightgray}
,
	framexleftmargin=2pt,
	framexrightmargin=2pt,
	framextopmargin=2pt,
	framexbottommargin=2pt,
	frame=single,
	basicstyle=\fontsize{10pt}{15pt}\selectfont,
	stepnumber=1,
	tabsize=4,
}


%increases table padding
\def\arraystretch{1.5}

\title{\textbf{CSCI-4113\\Assignment 2}}
\author{Anas Alhadi\\B00895875}

\begin{document}

	\maketitle
	\tableofcontents

	\newpage 

	\par{
	 	\textbf{\underline{Note:}} To avoid confusing myself, i redefined $y$ as $w$ 
		so the resulting LP $P$ is:
	}


	\begin{equation}\notag
		Minimize(3x+4w+2z)
	\end{equation}

	Such That:

	\begin{equation}\label{q1-1}\tag{1}
		4x+w-2z \leq 20
	\end{equation}
	\begin{equation}\tag{2}
		3x - w +z \ge 1 
	\end{equation}
	\begin{equation}\label{q1-3}\tag{3}
		x-2w+2z = -8
	\end{equation}
	\begin{equation}\tag{4}
		4x-w+3z \leq 21
	\end{equation}

	and
	
	\begin{equation}\notag
		x\ge 0
	\end{equation}
	\begin{equation}\notag
		w \le 0
	\end{equation}

	\newpage
	\section{Question 1}
	\par{Given the LP $P$ that is clearly not in Canonical Form as it has a 
	Minimization Objective Function, Lower Bound and equality Constriants, and negative/unbounded variables.\\We define a 
	sequence of equivalent LPs $P^{(i)}, 0\leq i\leq3$ such that $P^{(3)}=P'$ is an 
	LP equivalent to $P$ and in Canonical form:}


	\vspace{15pt}
	\textbf{\underline{First}}
	\par{
		We need to define an LP $P^{(0)}$ that is equivalent to $P$ but with the a negated
		Objective Function for $P^{(0)}$ to be a maximization LP. 
	}
	\begin{enumerate}
		\item Since $P$ and $P^{(0)}$ have the same variables and constraints, 
			this means that they have the same set of feasible solutions.
		\item Minimizing $f(x)$ is the same as maximizing $f'(x)$, thus $P$ and 
			$P'$ have the same Objective Function value.
	\end{enumerate}

	\par{
		$P^{(0)}$ will have an objective Function:
	}

	\begin{equation}\notag
		Maximize(-3x-4w-2z)
	\end{equation}

	\vspace{15pt}
	\textbf{\underline{Second}}
	\par{
		We now construct a new LP  $P^{(1)}$ that is equivalent to $P^{(0)}$ but with no
		equality constraints.\\ 
		That is, we replace all the equalities with inequalities.
		\begin{enumerate}
			\item Since $a=b$ is clearly equivalent to $a\le b$ \&\& $a \ge b$ 
			\item Thus $P^{(0)}$ and $P^{(1)}$ are equivalent since they have the same 
				set of variables, the same objective function and equivalent constraints.  
		\end{enumerate}
	}

	\par{
		Thus we replace constraint \hyperref[q1-3]{(3)} in $P^{(0)}$ with $\downarrow$ in $P^{(1)}$
	}

	\begin{equation}\label{q1-3.1}\tag{3.1}
		x-2w+2z \leq -8
	\end{equation}
	\begin{equation}\label{q1-3.2}\tag{3.2}
		x-2w+2z \ge -8
	\end{equation}

	\newpage
	\textbf{\underline{Third}}
	\par{
		The next step is to replace all the lower bound inequality constraints 
		in $P^{(1)}$ to upper bound constraints, thus constructing a new LP $P^{(2)}$.
	}

	\begin{enumerate}
		\item An inequality $a\le b$ is equivalent to its negation $-a \ge -b$
		\item Just like in the prev step, we are not changing the Objective function
			and replacing some constraints with equivalent one's thus both $P^{(2)}$ and 
			$P^{(1)}$ have the same Objective Function values and set of feasible solutions and are thus
			equivalent.
	\end{enumerate}

	\par{
		So we replace constraint \hyperref[q1-1]{(1)} and \hyperref[q1-3.2]{(3.2)} respectivley with:
	}

	\begin{equation}\tag{1.1}
		-3x+w-z \leq -1
	\end{equation}
	\begin{equation}\tag{3.2.1}
		-x+2w-2z \leq 8
	\end{equation}

	\par{This gives us an LP $P^{(2)}$}

	
	\vspace{15pt}
	\textbf{\underline{Fourth}}
	\par{
		We now need to add non-negativity constarints to $P^{(2)}$.
	}

	\begin{enumerate}
		\item $x$ already has the constraint so we dont need to modify it.
		\item \par{
			$w$ has a non-positivitey constraint, which is equivalent to:
			\begin{equation}\notag
				-w' \ge 0
			\end{equation}
			Thus we replace every instance of $w$ with $-w'$ (note that $w=w'$)
			and the constarint $w\leq 0$ with $w'\ge 0$.
		}

		\item \par{
				The variable $z$ is unbounded. We can add a non-negativitey constarint
				on it by representing it as the differnce of two non-negative numbers.
				It is clear to see that this holds for any number. So:

				\begin{equation}\notag
					z = z' - z''	
				\end{equation}
				And add the bellow constarints to the LP
				\begin{equation}\notag
					z'\ge0, z''\ge0
				\end{equation}
				We then replace all instances of $z$ with $z'-z''$ in $P^{(2)}$ Thus giving us a new LP $P^{(3)}$.
			}
	\end{enumerate}
	
	Notice that all the LP`s in the sequence {0,1,2,3} are equivalent and since $P$ is equivalent to $P^{(0)}$.
	This means that it is also equivalent to $P^{(3)}$. And since $P^{(3)}$ is a maximization 
	LP whom constraints all define upper bounds, and has non-negativitey constarints 
	on all its variables this means that it is in Canonical form, so $P=P^{(3)} = P'$)(The equality
	here denotes equivalence).

	\newpage
	Then $P'$ is our Canonical LP such that (im reusing equation numbers, a hard reset):

	\begin{equation}\notag
		Maximize(-3x+4w-2z'+2z'')
	\end{equation}
	Such that:
	\begin{equation}\tag{1}
		4x-w-2z'+2z''\leq20	
	\end{equation}
	\begin{equation}\tag{2}
		-3x-w-z'+z''\leq-1	
	\end{equation}
	\begin{equation}\tag{3}
		x+2w+2z'-2z''\leq-8
	\end{equation}
	\begin{equation}\tag{4}
		-x-2w-2z'+2z''\leq8	
	\end{equation}
	\begin{equation}\tag{5}
		4x+w+3z'-3z''\leq21	
	\end{equation}
	\begin{equation}\notag
		x\ge0, w\ge0, z'\ge0, z''\ge0	
	\end{equation}


	\newpage 
	\section{Question 2}
	\par{
		An LP is in standard form if it follows all the restrictions of the Canonical form
		with the changed restriction of having constarints be equality instead of inequalities.
		We do this by adding a slack variable $y_i$ for the $i^{th}$ constraint.\\ 
		So LP equivalent to $P$ and $P'$ but in standard form is $P''$ such that:
	}

	\begin{equation}\notag
		Maximize(-3x+4w'-2z'+2z'' +d)
	\end{equation}
	Such that:
	\begin{equation}\tag{1}
		4x-w-2z'+2z''+y_1=20	
	\end{equation}
	\begin{equation}\tag{2}
		-3x-w-z'+z''+y_2=-1	
	\end{equation}
	\begin{equation}\tag{3}
		x+2w+2z'-2z''+y_3=-8
	\end{equation}
	\begin{equation}\tag{4}
		-x-2w-2z'+2z''+y_4=8	
	\end{equation}
	\begin{equation}\tag{5}
		4x+w+3z'-3z''+y_5=21	
	\end{equation}
	\begin{equation}\notag
		x\ge0, w\ge0, z'\ge0, z''\ge0
	\end{equation}
	\begin{equation}
		y_i\ge0 \text{ where } 1\le i\le5	
	\end{equation}


	\newpage
	\section{Question 3}
	\begin{center}
		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
		\hline
		$b$& 	$y_1$& 	$y_2$& 	$y_3$& 	$y_4$& 	$y_5$& 	$x$& 	$w$& 	$z'$& 	$z''$\\
		\hline
		$20$& 	$1$& 	$$& 	$$& 	$$& 	$$& 	$4$& 	$-1$& 	$-2$& 	$2$\\		
		\hline
		$-1$& 	$$& 	$1$& 	$$& 	$$& 	$$& 	$-3$& 	$-1$& 	$-1$& 	$1$\\
		\hline
		$-8$& 	$$& 	$$& 	$1$& 	$$& 	$$& 	$1$& 	$2$& 	$2$& 	$-2$\\
		\hline
		$8$& 	$$& 	$$& 	$$& 	$1$& 	$$& 	$-1$& 	$-2$& 	$-2$& 	$2$\\ 
		\hline
		$21$& 	$$& 	$$& 	$$& 	$$& 	$1$& 	$4$& 	$1$& 	$3$& 	$-3$\\
		\hline
		$$& 	$$& 	$$& 	$$& 	$$& 	$$& 	$-3$& 	$4$& 	$-2$& 	$2$\\
		\hline
		\end{tabular}
	\end{center}

	\vspace{15pt}
	The basic solutions $\{b_1, b_2, b_3, b_4, b_5\}$ are $\{20, -1, -8, 8, 21\}$
	respectivley. This solution is not feasible since $b_1$ and $b_2$ both have 
	negative values.

	\newpage
	\section{Question 4}
	\par{
		We modify the Original LP by adding a new variable $s$ to form an Auxiliary LP $Q$:
	}

	\begin{equation}\notag
		Maximize(-s)
	\end{equation}
	Such that:
	\begin{equation}\tag{1}
		4x-w-2z'+2z''+y_1-s=20	
	\end{equation}
	\begin{equation}\tag{2}
		-3x-w-z'+z''+y_2-s=-1	
	\end{equation}
	\begin{equation}\tag{3}
		x+2w+2z'-2z''+y_3-s=-8
	\end{equation}
	\begin{equation}\tag{4}
		-x-2w-2z'+2z''+y_4-s=8	
	\end{equation}
	\begin{equation}\tag{5}
		4x+w+3z'-3z''+y_5-s=21	
	\end{equation}
	\begin{equation}\notag
		x\ge0, w\ge0, z'\ge0, z''\ge0, s\ge0
	\end{equation}
	\begin{equation}\notag
		y_i\ge0 \text{ where } 1\le i\le5	
	\end{equation}

	\vspace{15pt}
	\text{Giving us the following tableau}
	\begin{center}
		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
		\hline
		$b$& 	$y_1$& 	$y_2$& 	$y_3$& 	$y_4$& 	$y_5$& 	$x$& 	$w$& 	$z'$& 	$z''$& 	$s$\\
		\hline
		$20$& 	$1$& 	$$& 	$$& 	$$& 	$$& 	$4$& 	$-1$& 	$-2$& 	$2$& 	$-1$\\		
		\hline
		$-1$& 	$$& 	$1$& 	$$& 	$$& 	$$& 	$-3$& 	$-1$& 	$-1$& 	$1$& 	$-1$\\
		\hline
		$-8$& 	$$& 	$$& 	$1$& 	$$& 	$$& 	$1$& 	$2$& 	$2$& 	$-2$& 	$-1$\\
		\hline
		$8$& 	$$& 	$$& 	$$& 	$1$& 	$$& 	$-1$& 	$-2$& 	$-2$& 	$2$& 	$-1$\\ 
		\hline
		$21$& 	$$& 	$$& 	$$& 	$$& 	$1$& 	$4$& 	$1$& 	$3$& 	$-3$& 	$-1$\\
		\hline
		$$& 	$$& 	$$& 	$$& 	$$& 	$$& 	$-3$& 	$4$& 	$-2$& 	$2$& 	$-1$\\
		\hline
		\end{tabular}
	\end{center}


	\vspace{15pt}
	\textbf{\underline{Steps:}}
	\begin{enumerate}
		\item Choose the column whom basic variable corresponds to the lowest
			basic solution value. In our case the lowest value in $b$ is $-8$
			which corresponds to the variable $y_3$. So we swap them, $s$ enters the basis and $y_3$ leaves.
		\item  We now perform the bellow operations to restore the identity matrix:
			\begin{enumerate}
				\item (4) * -1
				\item (1) + (4)
				\item (2) + (4)
				\item (3) + (4)
				\item (5) + (4)
				\item (6) + (4)
			\end{enumerate}
		
			\newpage
			\text{This gives the bellow tableau:}
		\begin{center}
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				$b$& 	$y_1$& 	$y_2$& 	$s$& 	$y_4$& 	$y_5$& 	$x$& 	$w$& 	$z'$& 	$z''$& 	$y_3$\\
				\hline
				$28$& 	$1$& 	$$& 	$$& 	$$& 	$$& 	$3$& 	$-3$& 	$-4$& 	$4$& 	$-1$\\		
				\hline
				$7$& 	$$& 	$1$& 	$$& 	$$& 	$$& 	$-4$& 	$-3$& 	$-3$& 	$3$& 	$-1$\\
				\hline
				$8$& 	$$& 	$$& 	$1$& 	$$& 	$$& 	$-1$& 	$-2$& 	$-2$& 	$2$& 	$-1$\\
				\hline
				$16$& 	$$& 	$$& 	$$& 	$1$& 	$$& 	$-2$& 	$-4$& 	$-4$& 	$4$& 	$-1$\\ 
				\hline
				$29$& 	$$& 	$$& 	$$& 	$$& 	$1$& 	$2$& 	$-3$& 	$-1$& 	$1$& 	$-1$\\
				\hline
				$8$& 	$$& 	$$& 	$$& 	$$& 	$$& 	$-4$& 	$2$& 	$-4$& 	$4$& 	$-1$\\
				\hline
			\end{tabular}
		\end{center}


			Now we have that $Q$ has a feasible solution, so we continue solving the 
			LP until we find an optimal solution.

		\item Choose an arbirtary non-basic variable whom objective function
			value is non-negative, I'm choosing $z''$, we then find the row with 
			the $Min(\frac{b_i}{a_{z'',i}})$.\\ 
			In this case the min is $\frac{b_5}{a_{w,2}} = \frac{7}{3} = 2.333$

			So pivot $z''$ into the basis and $y_2$ out. Then perform the basic row operations to restore the 
			identity matrix in the basis.
			\begin{enumerate}
				\item (2) / 3
				\item (1) - 4*(2) 
				\item (3) - 2*(2)
				\item (4) - 4(2)
				\item (5) - (2)
				\item (6) - 4(2)
			\end{enumerate}

			Resulting in:
			\begin{center}
				\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
					\hline
					$b$& 				$y_1$& 	$z''$& 	$s$& 	$y_4$& 	$y_5$& 	$x$& 	$w$& 	$z'$& 	$y_2$& 	$y_3$\\
					\hline
					$\frac{56}{3}$& 	$1$& 	$$& 	$$& 	$$& 	$$& 	$\frac{25}{3}$& 	$1$& 	$$& 	$-\frac{4}{3}$& 	$\frac{1}{3}$\\		
					\hline
					$\frac{7}{3}$& 		$$& 	$1$& 	$$& 	$$& 	$$& 	$-\frac{4}{3}$& 	$-1$& 	$-1$& 	$\frac{1}{3}$& 	$-\frac{1}{3}$\\
					\hline
					$\frac{10}{3}$& 	$$& 	$$& 	$1$& 	$$& 	$$& 	$\frac{5}{3}$& 	$$& 	$$& 	$-\frac{2}{3}$& 	$-\frac{1}{3}$\\
					\hline
					$\frac{20}{3}$& 	$$& 	$$& 	$$& 	$1$& 	$$& 	$\frac{10}{3}$& 	$$& 	$$& 	$-\frac{4}{3}$& 	$\frac{1}{3}$\\ 
					\hline
					$\frac{80}{3}$& 	$$& 	$$& 	$$& 	$$& 	$1$& 	$\frac{10}{3}$& 	$-2$& 	$$& 	$-\frac{1}{3}$& 	$-\frac{2}{3}$\\
					\hline
					$\frac{10}{3}$& 	$$& 	$$& 	$$& 	$$& 	$$& 	$\frac{4}{3}$& 	$6$& 	$$& 	$-\frac{4}{3}$& 	$\frac{1}{3}$\\
					\hline
				\end{tabular}
			\end{center}


		\newpage
		\item Repeate steps 4 and 5, this time we pivot $x$ into the basis and $s$ out. 
			\begin{enumerate}
				\item (3) * 3/5
				\item (1) - 25/3(3)
				\item (2) + 4/3(3)
				\item (4) - 10/3(3)
				\item (5) - 10/3(3)
				\item (6) - 4/3(3)
			\end{enumerate}
		
			\begin{center}
				\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
					\hline
					$b$& 	$y_1$& 	$z''$& 	$x$& 	$y_4$& 	$y_5$& 	$s$& 	$w$& 	$z'$& 	$y_2$& 	$y_3$\\
					\hline
					$2$& 	$1$& 	$$& 	$$& 	$$& 	$$& 	$$& 	$1$& 	$$& 	$2$& 	$2$\\		
					\hline
					$5$& 	$$& 	$1$& 	$$& 	$$& 	$$& 	$$& 	$-1$& 	$-1$& 	$-\frac{1}{5}$& 	$-\frac{3}{5}$\\
					\hline
					$2$& 	$$& 	$$& 	$1$& 	$$& 	$$& 	$\frac{3}{5}$& 	$$& 	$$& 	$-\frac{2}{5}$& 	$-\frac{1}{5}$\\
					\hline
					$$& 	$$& 	$$& 	$$& 	$1$& 	$$& 	$-2$& 	$$& 	$$& 	$$& 	$1$\\ 
					\hline
					$20$& 	$$& 	$$& 	$$& 	$$& 	$1$& 	$-2$& 	$-2$& 	$$& 	$1$& 	$$\\
					\hline
					$$& 	$$& 	$$& 	$$& 	$$& 	$$& 	$-\frac{4}{5}$& 	$6$& 	$$& 	$-\frac{4}{5}$& 	$\frac{3}{5}$\\
					\hline
				\end{tabular}
			\end{center}


		\item Again now with $y_3$ as the variable entering the basis, the corresponding 
			variable to leave is $y_4$.

			\begin{enumerate}
				\item (1) - 2(4)  
				\item (2) + 3/5(4)  
				\item (3) + 1/5(4)  
				\item (6) - 3/5(4)  
			\end{enumerate}

			\begin{center}
				\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
					\hline
					$b$& 	$y_1$& 	$z''$& 	$x$& 	$y_3$& 	$y_5$& 	$s$& 	$w$& 	$z'$& 	$y_2$& 	$y_4$\\
					\hline
					$2$& 	$1$& 	$$& 	$$& 	$$& 	$$& 	$4$& 	$1$& 	$$& 	$2$& 	$-2$\\		
					\hline
					$5$& 	$$& 	$1$& 	$$& 	$$& 	$$& 	$-\frac{6}{5}$& 	$-1$& 	$-1$& 	$-\frac{1}{5}$& 	$\frac{3}{5}$\\
					\hline
					$2$& 	$$& 	$$& 	$1$& 	$$& 	$$& 	$\frac{1}{5}$& 	$$& 	$$& 	$-\frac{2}{5}$& 	$\frac{1}{5}$\\
					\hline
					$$& 	$$& 	$$& 	$$& 	$1$& 	$$& 	$-2$& 	$$& 	$$& 	$$& 	$1$\\ 
					\hline
					$20$& 	$$& 	$$& 	$$& 	$$& 	$1$& 	$-2$& 	$-2$& 	$$& 	$1$& 	$$\\
					\hline
					$$& 	$$& 	$$& 	$$& 	$$& 	$$& 	$\frac{2}{5}$& 	$6$& 	$$& 	$-\frac{4}{5}$& 	$-\frac{3}{5}$\\
					\hline
				\end{tabular}
			\end{center}

		\newpage
		\item Again this time $w$ enters the basis, and $y_1$ leaves. 
			\begin{enumerate}
				\item (2) + (1)
				\item (5) + 2(1)
				\item (6) - 6(1)
			\end{enumerate}

			\begin{center}
				\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
					\hline
					$b$& 	$w$& 	$z''$& 	$x$& 	$y_3$& 	$y_5$& 	$s$& 	$y_1$& 	$z'$& 	$y_2$& 	$y_4$\\
					\hline
					$2$& 	$1$& 	$$& 	$$& 	$$& 	$$& 	$4$& 	$1$& 	$$& 	$2$& 	$-2$\\		
					\hline
					$7$& 	$$& 	$1$& 	$$& 	$$& 	$$& 	$\frac{14}{5}$& 	$1$& 	$-1$& 	$\frac{9}{5}$& 	$-\frac{7}{5}$\\
					\hline
					$2$& 	$$& 	$$& 	$1$& 	$$& 	$$& 	$\frac{1}{5}$& 	$$& 	$$& 	$-\frac{2}{5}$& 	$\frac{1}{5}$\\
					\hline
					$$& 	$$& 	$$& 	$$& 	$1$& 	$$& 	$-2$& 	$$& 	$$& 	$$& 	$1$\\ 
					\hline
					$24$& 	$$& 	$$& 	$$& 	$$& 	$1$& 	$6$& 	$2$& 	$$& 	$5$& 	$-4$\\
					\hline
					$$& 	$$& 	$$& 	$$& 	$$& 	$$& 	$-\frac{118}{5}$& 	$-6$& 	$$& 	$-\frac{64}{5}$& 	$\frac{57}{5}$\\
					\hline
				\end{tabular}
			\end{center}



		\item Again, now $y_4$ enters and $y_3$ leaves the basis 
			\begin{enumerate}
				\item (1) + 2(4) 
				\item (2) + 7/5(4) 
				\item (3) - 1/5(4) 
				\item (5) + 4(4) 
				\item (6) -57/5(4) 
			\end{enumerate}

			\begin{center}
				\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
					\hline
					$b$& 	$w$& 	$z''$& 	$x$& 	$y_4$& 	$y_5$& 	$s$& 	$y_1$& 	$z'$& 	$y_2$& 	$y_3$\\
					\hline
					$2$& 	$1$& 	$$& 	$$& 	$$& 	$$& 	$$& 	$1$& 	$$& 	$2$& 	$2$\\		
					\hline
					$7$& 	$$& 	$1$& 	$$& 	$$& 	$$& 	$$& 	$1$& 	$-1$& 	$\frac{9}{5}$& 	$\frac{7}{5}$\\
					\hline
					$2$& 	$$& 	$$& 	$1$& 	$$& 	$$& 	$\frac{3}{5}$& 	$$& 	$$& 	$-\frac{2}{5}$& 	$-\frac{1}{5}$\\
					\hline
					$$& 	$$& 	$$& 	$$& 	$1$& 	$$& 	$-2$& 	$$& 	$$& 	$$& 	$1$\\ 
					\hline
					$24$& 	$$& 	$$& 	$$& 	$$& 	$1$& 	$-2$& 	$$& 	$2$& 	$$& 	$4$\\
					\hline
					$$& 	$$& 	$$& 	$$& 	$$& 	$$& 	$-\frac{4}{5}$& 	$-6$& 	$$& 	$-\frac{64}{5}$& 	$-\frac{57}{5}$\\
					\hline
				\end{tabular}
			\end{center}


		\item We now remove $s$ and recover the original objective function values of $x,w,z',z''$ and 
			perform the following row operations to fix the basis:

			\begin{center}
				\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
					\hline
					$b$& 	$w$& 	$z''$& 	$x$& 	$y_4$& 	$y_5$& 	$y_1$& 	$z'$& 	$y_2$& 	$y_3$\\
					\hline
					$2$& 	$1$& 	$$& 	$$& 	$$& 	$$&  	$1$& 	$$& 	$2$& 	$2$\\		
					\hline
					$7$& 	$$& 	$1$& 	$$& 	$$& 	$$&  	$1$& 	$-1$& 	$\frac{9}{5}$& 	$\frac{7}{5}$\\
					\hline
					$2$& 	$$& 	$$& 	$1$& 	$$& 	$$& 	$$& 	$$& 	$-\frac{2}{5}$& 	$-\frac{1}{5}$\\
					\hline
					$$& 	$$& 	$$& 	$$& 	$1$& 	$$& 	$$& 	$$& 	$$& 	$1$\\ 
					\hline
					$24$& 	$$& 	$$& 	$$& 	$$& 	$1$& 	$$& 	$2$& 	$$& 	$4$\\
					\hline
					$$& 	$4$& 	$2$& 	$-3$& 	$$& 	$$& 	$-6$& 	$-2$& 	$-\frac{64}{5}$& 	$-\frac{57}{5}$\\
					\hline
				\end{tabular}
			\end{center}

		\item Finally perform last set of row operations: 			
			\begin{enumerate}
				\item (6) - 4(1)
				\item (6) - 2(2)
				\item (6) + 3(3)	
			\end{enumerate}
		The final LP is:
			\begin{center}
				\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
					\hline
					$b$& 	$w$& 	$z''$& 	$x$& 	$y_4$& 	$y_5$& 	$y_1$& 	$z'$& 	$y_2$& 	$y_3$\\
					\hline
					$2$& 	$1$& 	$$& 	$$& 	$$& 	$$&  	$1$& 	$$& 	$2$& 	$2$\\		
					\hline
					$7$& 	$$& 	$1$& 	$$& 	$$& 	$$&  	$1$& 	$-1$& 	$\frac{9}{5}$& 	$\frac{7}{5}$\\
					\hline
					$2$& 	$$& 	$$& 	$1$& 	$$& 	$$& 	$$& 	$$& 	$-\frac{2}{5}$& 	$-\frac{1}{5}$\\
					\hline
					$$& 	$$& 	$$& 	$$& 	$1$& 	$$& 	$$& 	$$& 	$$& 	$1$\\ 
					\hline
					$24$& 	$$& 	$$& 	$$& 	$$& 	$1$& 	$$& 	$2$& 	$$& 	$4$\\
					\hline
					$-16$& 	$$& 	$$& 	$$& 	$$& 	$$& 	$-12$& 	$$& 	$-\frac{128}{5}$& 	$-\frac{114}{5}$\\
					\hline
				\end{tabular}
			\end{center}
	\end{enumerate}


	\newpage
	\section{Question 5}
	\textbf{\underline{Steps:}}
	\begin{itemize}
		\item The tableau we get from Q4) can not be optimized any further as we have that all the coefficients in the objective function 
			as negative values.
		\item The BFS values we get are: $x=2, w=2, z'=0, z''=7$ with the Objective function value being $16$.
		\item The solution of the original LP is: $3(2)+4(-2)+2(0-7) = -16$
	\end{itemize}

	\newpage 
	\section{Question 6}
		\textbf{\underline{Brief Overview/Definitions:}}
		\begin{enumerate}
			\item At every run, Simplex attempts to increase the value of a non-basic 
					variable by the tightest upper bound imposed on the variable by the constraints. 
			\item Recall that in the notes, we stated that the feasible region of every individual constarint forms a 
				half space, and since a feasible solution must satisfy all constraints this means that it lies in the 
				intersection of these halfspaces which is a convex polytope. (I focus on the fact that the feasible region is convex)
		\end{enumerate}

		\textbf{\underline{Proof}}
		\par{Given a tablue in which all the coefficients in the objective function are negative, this means that increasing the 
				value of any of the non-basic variables will reduce the objective function value.}
		\par{Further, since the feasible region of our tablue is convex this means that a local maxima on the objective function is also a 
		global maxima. Thus the solution can not be ``pushed up" any further without breaking any of the constraints. And the BFS 
		at the point where the coefficients of the objective function are all negative is an optimal solution for that tablue.}
		
		\par{Finally since Simplex always constructs tablues with the same objective function and equivalent constraints to that 
				of the original LP, means that for a feasible solution of the original LP say $z'$ to have an objective function value 
				larger than $\hat{z}$ implies that the tablue constructed by simplex is not equivalent to the original LP, since 
				we know that $\hat{z}$ is at a golbal maxima of it's feasibility region so $z'$ must have a different feasibility region.
				And since we only use basic row operations when constructing subsequent tablues we know that this is not true. }

\end{document}
